openarchaeoCollaboration

### 2021-05-11 analysis/paper.Rmd
Preliminary notes for background section.
Also updated the bib file, which now contains the sources mentioned in the notes.

>>>>

## Background

- Lots of reviews out there on sets of tools geared towards specific kinds of applications
  - i.e. for aerial photo recognition, for photogrammetry, for tablet data collection, etc

- A few papers encouraging use of open source tools and platforms
  - @schmidt2020, @ducke2012, @orengo2015, @ducke2015, @ross2015, @wells2015

- @jeffrey2012, @beck2012, @bevan2012 on the new kinds of engagements and commitments that openness entails
  - @hansen2019 on the structural/systemtic challenges involved in maintaining a proper archaeological database
  - @parsons2013, @kansa2014a on carrying over existing ideas and modes of production

- On community-building
  - @carman2017 on the community-building and @carman2006 on the social practice of digging; we might extend this to discuss extended network of archaeological practices, which now includes software development
  - @morgan2012, @richardson2017b, @huggett2004 on encouraging wider participation within open collaboration networks
  - @morgan2015 and @caraher2019 on anarchic ethos in archaeology, see also responses by @richardson2017; we might draw parallels with similar worldviews in open source software development (i.e. hacker and DIY culture)
  - @sholler2019 wrote a general guide for encouraging participation within open source research projects (but not as an archaeologist)

- @daems2020 on educating students to use digital tools, and @morgan2018a on problems with making tools easy to use (relates to @caraher2015's value of friction)
  - Might also draw from @graham2019 and @graham2020 on pedagogical and exploratory aspects of hacking away
